Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-05 article-models-ttderived.tex
terms as sections

>>>>

Note that we can directly view any term $x$ of $A$ in context $\Gamma$ as a
morphism from the empty family $\emptyf$ to $A$ in context $\Gamma$.

Now let $\jterm{{\Gamma}{A}}{P}{f}$ be a term of $P$. Then we can view $f$ as a
morphism from $A$ to $\ctxext{A}{P}$ in the following way:

\begin{defn}
Let $\jterm{{\Gamma}{A}}{P}{f}$ be a term. Then we define
\begin{equation*}
\jhomdefn{\Gamma}{A}{{A}{P}}{\jtermashom{f}}{\unfold{\jtermashom{f}}}
\end{equation*}
\end{defn}

In the following lemma we will see that $\jtermashom{f}$ is a section for
$\cprojfstf{A}{P}$.

\begin{lem}
Consider a family $\jfam{{\Gamma}{A}}{P}$ and a term $\jterm{\Gamma}{A}{x}$.
Then we have the judgmental equality
\begin{equation*}
\jhomeq{\Gamma}{A}{A}{\jcomp{A}{\jtermashom{f}}{\cprojfstf{A}{P}}}{\idtm{A}}.
\end{equation*}
\end{lem}

\begin{proof}
We have the judgmental equalities
\begin{align*}
\jtermashom{f}
& \jdeq
  \unfold{\jtermashom{f}}
  \tag{by definition}
  \\
& \jdeq
  \jcomp{}{f}{\jcomp{}{\idtm{A}}{\cprojfstf{A}{P}}}
  \tag{by \autoref{lem:composition-threesome}}
  \\
& \jdeq
  \jcomp{}{f}{\cprojfstf{A}{P}}
  \tag{by \autoref{lem:jcomp-idtm}}
  \\
& \jdeq
  \jcomp{}{f}{\ctxwk{P}{\idtm{A}}}
\end{align*}
\end{proof}
